Contextual Combinatorial Cascading Bandits

### 2016-02-02 contextual combinatorial cascading bandits.tex
update proof

\newcommand{\CLemmaPrefixExi}{
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
	$$
	p_{t, B} \geq \frac{1}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R(t, B) \geq \frac{1}{2} R(t, A).
	$$ 
}
\newcommand{\CEqDeltaEstAnd}{
	$$
	\EE [R(t, \bA_t) |\cH_t ] \leq \frac{8}{f^{\ast}} \EE \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} | \cH_t\right].
	$$
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and $B$-Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
	\end{align}
	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
\end{theorem}
The regret bound deteriorates as $p^*$ gets small. But unfortunately, this reciprocal dependence on $p^*$ is not known how to improve, even in the special case of disjunctive objective. Indeed, in that case, the bound in Section 2.3 of \cite{kveton2015combinatorial} also has a reciprocal dependence on $p^*$. However, in the special case of conjunctive objective, we will give an improved bound, like \cite{kveton2015combinatorial} does.

@@

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). \label{eq:OrRewardFunc}
\end{align}
It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity. (All verifications are left in the Appendix.) 
%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. 
We have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
	\begin{align}
		R^{\alpha}(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) \nonumber \\
		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	We will prove it in the Appendix. The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

Now we are ready to prove the main theorem.

\begin{proof}[ of Theorem \ref{thm:main}]
	Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is true with probability $1-\delta$. Then we have
	\begin{align}
	&R^{\alpha}(n) = \EE \left[\sum_{t=1}^{n} \EE[R^{\alpha}(t, \bA_t) | \cH_t] \right] \notag\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \EE \left[ \left. \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right| \cH_t \right] \right] \label{eq:pfMdeltaEst}\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \bbeta_{n}(\delta) \EE \left[ \left. \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right] \right] \label{eq:pfMbeta}\\
	&\leq \EE \left[\frac{B}{p^*} \bbeta_n(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
	&\leq \EE\left[\frac{B}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d / n} \right)} + \sqrt{\lambda} \right) \right. \notag\\
	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
	&\leq \frac{\sqrt{2}B}{p^*} \left(R\sqrt{ \ln[ (1 + C_\gamma n/(\lambda d))^d n ]} + \sqrt{\lambda} \right) \notag\\
	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMdetEst}
	\end{align}
	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
\end{proof}

@@

In this section, we prove the expected reward function
$$
f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
$$
where $A = (a_1, \ldots, a_{|A|})$, defined in~Eq.\eqref{eq:OrRewardFunc}, satisfies the properties of monotonicity and Lipschitz continuity.

\begin{lemma}[monotonicity]
	\label{lem:orMonotonicity}
	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$. Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
	$$
	f(A, w) \leq f(A, w').
	$$
\end{lemma}
\begin{proof}
	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, for $1 \leq k \leq m$, we have
	\begin{align*}
		&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
		\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
		\geq &~\gamma_{k} \cdot 0 = 0.
	\end{align*}
	Then it implies that
	\begin{align*}
		&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
		\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
	\end{align*}
	Therefore, 
	\begin{align*}
		& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
		&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
		&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
		&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
		&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
		&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
	\end{align*}
\end{proof}

\begin{lemma}[Lipschitz continuity]
	\label{lem:orLip}
	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
	$$
	|f(A, w) - f(A, w')| \leq \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
	$$
	where $A = (a_1, \ldots, a_{|A|})$.
\end{lemma}
\begin{proof}
	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, suppose $w \leq w'$ and $w' = w + v$.

@@

	For general $w,w' \in [0,1]^L$, by last lemma, we have
	$$
	f(A, w\wedge w') \leq f(A, w), f(A, w') \leq f(A, w\vee w'),
	$$
	where 
	$$
	(w\wedge w')_k = \min\{w_k, w'_k\}, ~ (w\vee w')_k = \max\{w_k, w'_k\}.
	$$
	Then
	\begin{align*}
		&|f(A,w) - f(A,w')| \leq f(A, w\vee w') - f(A, w\wedge w')\\
		\leq & \sum_{k=1}^{|A|} \gamma_k [(w\vee w')(a_k) - (w\wedge w')(a_k)]\\
		=& \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|
	\end{align*}
\end{proof}

We have proved the monotonicity and Lipschitz continuity of expected reward function $f$. Then by Theorem \ref{thm:main}, the corollary can be obtained.

@@

In this section, we prove Theorem \ref{thm:and}. Recall the expected reward function is
$$
f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
$$
where $A = (a_1, \ldots, a_{|A|})$, as defined in~Eq.\eqref{eq:AndRewardFunc}. First, similar to last section, we prove this reward function satisfies the properties of monotonicity and Lipschitz continuity.

\begin{lemma}[monotonicity]
	\label{lem:andMonotonicity}
	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$. Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
	$$
	f(A, w) \leq f(A, w').
	$$
\end{lemma}
\begin{proof}
	Denote $A = (a_1, \ldots, a_{|A|})$. Because
	\begin{align*}
	&1 - f(A, 1-w) \\
	=& 1- \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} (1-w(a_i))w(a_k) - \prod_{i=1}^{\abs{A}}(1-w(a_i))\\
	=& \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
	\end{align*}
	then by the proof of Lemma \ref{lem:orMonotonicity} and $1-f(A,1-w)$ is increasing in $w$, we can get $f$ is increasing in $w$.
\end{proof}

\begin{lemma}[Lipschitz continuity]
	\label{lem:andLip}
	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
	$$
	|f(A, w) - f(A, w')| \leq \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
	$$
	where $A = (a_1, \ldots, a_{|A|})$.
\end{lemma}
\begin{proof}
	Similar to the proof of Lemma \ref{lem:orLip}. It is enough to prove when $w \leq w', w' = w + v $ and $A = (1, \ldots, m), m \leq K$.

@@

\begin{lemma} %lem:prefixexists
	\label{lem:prefixexists}
	\CLemmaPrefixExi
\end{lemma}
\begin{proof}
	$w_t = \theta_*^{\top} x_t$. If $f(A, w_t) \geq \frac{1}{2} f_{t}^{\ast}$, then by Lemma \ref{lem:prefixRelation} (1),
	$$
	p_{t, A} \geq \frac{1}{2} f_{t}^{\ast} - 1 + \gamma_{\abs{A}}.
	$$
	In this case, we set prefix $B = A$.

>>>>

\newcommand{\CLemmaPrefixExi}{
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
	$$
	p_{t, B} \geq \frac{\alpha}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R^{\alpha}(t, B) \geq \frac{1}{2} R^{\alpha}(t, A).
	$$ 
}
\newcommand{\CEqDeltaEstAnd}{
	$$
	\EE [R^{\alpha}(t, \bA_t) |\cH_t ] \leq \frac{8}{\alpha f^{\ast}} \EE \left[ \left. \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t\right].
	$$
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and $B$-Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) + \sqrt{n}\nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
	\end{align}
	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
\end{theorem}
The regret bound deteriorates as $p^*$ gets small. But unfortunately, this reciprocal dependence on $p^*$ is not known how to improve, even in the special case of disjunctive objective. Indeed, in that case, the bound in Section 2.3 of \cite{kveton2015combinatorial} also has a reciprocal dependence on $p^*$. However, in the special case of conjunctive objective, we will give an improved bound, like \cite{kveton2015combinatorial} does.

@@

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). \label{eq:OrRewardFunc}
\end{align}
It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity. (All verifications are left in the Appendix.) 
%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. 
We have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \sqrt{n}\nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{\alpha}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
	\begin{align}
		R^{\alpha}(n) \le& \frac{\sqrt{128}}{\alpha f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) + \alpha \sqrt{n} \nonumber \\
		=&O\left(\frac{d}{\alpha f^{\ast}}\sqrt{nK} \ln(C_{\gamma} n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	We will prove it in the Appendix. The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

Lemma \ref{lem:SumXiEstimateInDet} and Lemma \ref{lem:detVt} combined imply Lemma \ref{lem:XNormSumEst}. Now we are ready to prove the main theorem.

\begin{proof}[ of Theorem \ref{thm:main}]
	Suppose Ineq.~\eqref{eq:estimateTheta} holds for all time $t$, which is true with probability $1-\delta$. Then with probablity $1-\delta$, we have
	\begin{align}
	&R^{\alpha}(n) = \EE \left[\sum_{t=1}^{n} \EE[R^{\alpha}(t, \bA_t) | \cH_t] \right] \notag\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{2B}{p^*} \EE \left[ \left. \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right| \cH_t \right] \right] \label{eq:pfMdeltaEst}\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{2B}{p^*} \bbeta_{n}(\delta) \EE \left[ \left. \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right] \right] \label{eq:pfMbeta}\\
	&\leq \EE \left[\frac{2B}{p^*} \bbeta_n(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
	&\leq \EE\left[\frac{2B}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d / n} \right)} + \sqrt{\lambda} \right) \right. \notag\\
	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
	&\leq \frac{2\sqrt{2}B}{p^*} \left(R\sqrt{ \ln[ (1 + C_\gamma n/(\lambda d))^d n ]} + \sqrt{\lambda} \right) \notag\\
	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMdetEst}
	\end{align}
	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.

	Also $R^{\alpha}(n) \leq n$ and $\delta = \frac{1}{\sqrt{n}}$. We have 
	\begin{align*}
		R^{\alpha}(n) &\leq \frac{2\sqrt{2}B}{p^*} \left(R\sqrt{ \ln[ (1 + C_\gamma n/(\lambda d))^d n ]} + \sqrt{\lambda} \right) \\
		&\qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} + \sqrt{n}.
	\end{align*}
\end{proof}

@@

In this section, we prove the expected reward function
$$
f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
$$
where $A = (a_1, \ldots, a_{|A|})$, defined in~Eq.\eqref{eq:OrRewardFunc}, satisfies the properties of monotonicity and $1$-Lipschitz continuity.

\begin{lemma}[monotonicity]
	\label{lem:orMonotonicity}
	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$. Then $f(A, w)$ is increasing with respect to $w$, that is, if $w \leq w' \in [0,1]^E$, then for any $A \in \prod^{\leq K}$, it holds that
	$$
	f(A, w) \leq f(A, w').
	$$
\end{lemma}
\begin{proof}
	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. Denote $w = (w_a)_{a \in E}$ and $w' = (w'_a)_{a \in E}$. First, for $1 \leq k \leq m$, we have
	\begin{align*}
		&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
		\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
		\geq &~\gamma_{k} \cdot 0 = 0.
	\end{align*}
	Then it implies that
	\begin{align*}
		&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
		\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
	\end{align*}
	Therefore, 
	\begin{align*}
		& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
		&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
		&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
		&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
		&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
		&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
	\end{align*}
\end{proof}

\begin{lemma}[Lipschitz continuity]
	\label{lem:orLip}
	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{E}$. Then
	$$
	|f(A, w) - f(A, w')| \leq \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
	$$
	where $A = (a_1, \ldots, a_{|A|})$.
\end{lemma}
\begin{proof}
	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. Denote $w = (w_a)_{a \in E}$ and $w' = (w'_a)_{a \in E}$. First, suppose $w \leq w'$ and $w' = w + v$.

@@

	For general $w,w' \in [0,1]^L$, by Lemma \ref{lem:orMonotonicity}, we have
	$$
	f(A, w\wedge w') \leq \{f(A, w), f(A, w') \}\leq f(A, w\vee w'),
	$$
	where 
	$$
	(w\wedge w')_k = \min\{w_k, w'_k\}, ~ (w\vee w')_k = \max\{w_k, w'_k\}.
	$$
	Then
	\begin{align*}
		&|f(A,w) - f(A,w')| \leq f(A, w\vee w') - f(A, w\wedge w')\\
		\leq & \sum_{k=1}^{|A|} \gamma_k [(w\vee w')(a_k) - (w\wedge w')(a_k)]\\
		=& \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|
	\end{align*}
\end{proof}

We have proved the monotonicity and Lipschitz continuity of expected reward function $f$. Then the corollary follows Theorem \ref{thm:main}.

@@

In this section, we prove Theorem \ref{thm:and}. Recall the expected reward function is
$$
f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
$$
where $A = (a_1, \ldots, a_{|A|})$, as defined in~Eq.\eqref{eq:AndRewardFunc}. First, similar to last section, we prove this reward function satisfies the properties of monotonicity and $1$-Lipschitz continuity.

\begin{lemma}[monotonicity]
	\label{lem:andMonotonicity}
	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$. Then $f(A, w)$ is increasing with respect to $w$; that is, if $w \leq w' \in [0,1]^E$, then for any $A \in \prod^{\leq K}$, it holds that
	$$
	f(A, w) \leq f(A, w').
	$$
\end{lemma}
\begin{proof}
	Denote $A = (a_1, \ldots, a_{|A|})$. Because
	\begin{align*}
	&1 - f(A, 1-w) \\
	=& 1- \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} (1-w(a_i))w(a_k) - \prod_{i=1}^{\abs{A}}(1-w(a_i))\\
	=& \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
	\end{align*}
	then by the proof of Lemma \ref{lem:orMonotonicity} and $1-f(A,1-w)$ is increasing in $w$, we can get $f$ is increasing in $w$.
\end{proof}

\begin{lemma}[Lipschitz continuity]
	\label{lem:andLip}
	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
	$$
	|f(A, w) - f(A, w')| \leq \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
	$$
	where $A = (a_1, \ldots, a_{|A|})$.
\end{lemma}
\begin{proof}
	Denote $w = (w_a)_{a \in E}$ and $w' = (w'_a)_{a \in E}$. Similar to the proof of Lemma \ref{lem:orLip}. It is enough to prove when $w \leq w', w' = w + v $ and $A = (1, \ldots, m), m \leq K$.

@@

\begin{lemma} %lem:prefixexists
	\label{lem:prefixexists}
	\CLemmaPrefixExi
\end{lemma}
\begin{proof}
	Recall $w_t = \theta_*^{\top} x_t$. If $f(A, w_t) \geq \frac{\alpha}{2} f_{t}^{\ast}$, then by Lemma \ref{lem:prefixRelation} (1),
	$$
	p_{t, A} \geq \frac{\alpha}{2} f_{t}^{\ast} - 1 + \gamma_{\abs{A}}.
	$$
	In this case, we set prefix $B = A$.

	Now suppose $f(A, w_t) \leq \frac{\alpha}{2} f_{t}^{\ast}$. Let
	$$
	x_k = f(B_k,w), ~~ y_k = 1 - \gamma_k + \gamma_k p_{t,B_k}, ~~I_k = [x_k, y_k]
	$$
	Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$. Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$. Also, $x_{\abs{A}} = f(A, w)$ and $y_1 = 1$. Thus
	$$
	[f(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
	$$
	Then there exists a $k$ such that $\frac{\alpha}{2}f_{t}^{\ast} \in I_k$:
	$$
	f(B_k,w) \leq \frac{\alpha}{2}f_{t}^{\ast} \leq 1 - \gamma_k + \gamma_k p_{t, B_k}
	$$
	Then 
	$$
	R^{\alpha}(t,B_k) = \alpha f_t^* - f(B_k, w_t) \geq \frac{\alpha}{2}f_t^* \geq \frac{1}{2} R^{\alpha}(A, w_t),
	$$
	and
	$$
	p_{t, B_k} \geq \frac{\alpha}{2}f_t^* - 1 + \gamma_{|B_k|}.
	$$
\end{proof}
